\Title

### 2021-01-18 manuscript/manuscript.tex
Advance on manuscript

Our final goal is to show how gradient-boosted equivalent sources can be used
to interpolate a very large dataset of gravity data into a regular grid.
We selected a compilation of gravity surveys over Australia made by
\citet{wynne2018}.
It consists in more than 1.7 million data points that cover most part of the
Australia territory obtained through observations on ground
(see Fig.~\ref{fig:australia-data}).

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-data-gravity.png}
    \caption{
    }
    \label{fig:australia-data-gravity}
\end{figure*}

First we compute the gravity disturbance by removing the normal gravity from
the observed gravity data (see Fig.~\ref{fig:australia-disturbance}).
The normal gravity is computed on each observation point through the
closed-form formula given by \citet{li2001} and using the WGS84 ellipsoid as
reference.
Then we obtain plain coordinates of the observation points by applying
a Mercator projection.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-data-disturbance.png}
    \caption{
    }
    \label{fig:australia-data-disturbance}
\end{figure*}

We start the interpolation process by defining a set of block-averaged sources
at a relative depth of \AustraliaEqlDepth{}.
The choice of the block spacing must be done taking into account the desired
resolution of the final grid.
If the grid will have a much higher resolution than the block spacing, the
equivalent sources will not be able to reproduce the high frequency components
of the data.
Therefore we recommend setting a block spacing that matches the resolution of
the final grid.
In this case we will generate a regular grid with a resolution of 1~arc-minute,
which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-grid.png}
    \caption{
    }
    \label{fig:australia-grid}
\end{figure*}

>>>>

Our final goal is to show how gradient-boosted equivalent sources can be used
to interpolate a very large dataset of gravity data into a regular grid.
We selected a compilation of gravity surveys over Australia made by
\citet{wynne2018}.
It consists in more than 1.7 million data points that cover most part of the
Australia territory obtained through observations on ground
(see Fig.~\ref{fig:australia-data-gravity}).

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-data-gravity.png}
    \caption{
        Gravity data for Australia composed by more than 1.7 million
        observations on ground \citep{wynne2018}. The data is available under
        the Creative Commons Attribution 4.0 International Licence.
    }
    \label{fig:australia-data-gravity}
\end{figure*}

First we compute the gravity disturbance by removing the normal gravity from
the observed gravity data (see Fig.~\ref{fig:australia-data-disturbance}).
The normal gravity is computed on each observation point through the
closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
as reference.
Then we obtain plain coordinates of the observation points by applying
a Mercator projection.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-data-disturbance.png}
    \caption{
        Gravity disturbance of Australia computed as the difference between
        observed gravity and normal gravity generated by the WGS84 ellipsoid on
        each observation point.
    }
    \label{fig:australia-data-disturbance}
\end{figure*}

We start the interpolation process by defining a set of block-averaged sources
at a relative depth of \AustraliaEqlDepth{} and a block spacing of
\SI{1.8}{\kilo\meter}.
These parameters create \AustraliaEqlNSources{}~point sources.
The choice of the block spacing must be done taking into account the desired
resolution of the final grid.
If the grid will have a much higher resolution than the block spacing, the
equivalent sources will not be able to reproduce the high frequency components
of the data.
Therefore we recommend setting a block spacing that matches the resolution of
the final grid.
In this case we will generate a regular grid with a resolution of 1~arc-minute,
which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.

The coefficients of the gradient-boosted equivalent sources are estimated using
a damping equal to \AustraliaEqlDamping{} and a window size of
\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
store the largest Jacobian matrix to 10GB.

Finally, the equivalent sources are used to predict the values of the gravity
disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid
(see Fig.~\ref{fig:australia-grid}).

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-grid.png}
    \caption{
        Interpolated gravity disturbance of Australia on a regular grid at
        \AustraliaEqlGridHeight{} over the ellipsoid. The interpolated values
        were obtained through gradient-boosted equivalent sources.
    }
    \label{fig:australia-grid}
\end{figure*}
